Technique for \earlywarning\ filtering for compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-29 conclusions.tex
softened comp reqs a bit
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1201 ccdd05d5-56c1-461a-bf98-85f6876523b4

The \lloid{} method is as fast as standard \fft{} convolutions but allows for a
technically latency-free, real-time operation.  We anticipate requiring
$\gtrsim 4 \times 10 = 40$ modern multi-core computers to search for binary
neutron stars using coincident \GW\ data from a four-detector network.  In the
future, additional computational savings could be acheived by conditionally
reconstructing the \SNR{} time-series only during times when a composite
detection statistic crosses a threshold~\citep{svd-compdetstat}.  However, the
anticipated required number of computers is well within the current computing
capabilities of the \LIGO{} Data
Grid\footnote{\url{https://www.lsc-group.phys.uwm.edu/lscdatagrid/}}.

>>>>

The \lloid{} method is as fast as standard \fft{} convolutions but allows for a
technically latency-free, real-time operation.  We anticipate requiring $\sim
100$ modern multi-core computers to search for binary neutron stars using
coincident \GW\ data from a multi-detector network.  In the future, additional
computational savings could be acheived by conditionally reconstructing the
\SNR{} time-series only during times when a composite detection statistic
crosses a threshold~\citep{svd-compdetstat}.  However, the anticipated required
number of computers is well within the current computing capabilities of the
\LIGO{} Data
Grid\footnote{\url{https://www.lsc-group.phys.uwm.edu/lscdatagrid/}}.
